TITLE

### 2021-02-17 outputs/paper/data_simulation.Rmd
stitching together simulation work and tidying file names

```{r}
# read in the data
# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame must have been run already

@@

survey_1 <- table_for_surveys %>%
  select(ID, group) %>%
  arrange(ID)

@@

# Type of service provided
LORENA
## Survey 1
```{r}
survey_1 <- survey_1 %>%
```

# Demographic traits of owners
AMY AND LALA

@@

```{r}
set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))

@@

####################33 THIS WONT WORK UNTIL LORENA"S PART IS ADDED ON TYPE
survey_2 <-
  bind_rows(
    survey_2 %>%
      filter(type == "dinein" & group == "treatment") %>%
      mutate(revenue = 0.55 * revenue)
    ,
    survey_2 %>%
      filter(type == "both" & group == "treatment") %>%
      mutate(revenue = 0.83 * revenue)
    ,
    survey_2 %>%
      filter(type == "takeout" & group == "treatment") %>%
      mutate(revenue = revenue)
    ,
    survey_2 %>%
      filter(group == "control")
  ) %>%
  arrange(ID)

>>>>

```{r}
# read in the data
# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame must have been run already

@@

survey_1 <- table_for_surveys %>%
  select(ID, group, verify) %>%
  arrange(ID)

@@

# Type of service provided
```{r}
# Read in data
yelp_data <- read_csv(here("inputs/data/yelp_restaurants_ontario.csv")) %>% 
  na.omit() # Remove all NAs
total_restaurants <- count(yelp_data)

# Check proportion of RestaurantsTakeOut
takeout <- yelp_data %>% 
  select(RestaurantsTakeOut)
summary(takeout)
```
```{r}
takeout_percentage <- takeout %>%
  group_by(RestaurantsTakeOut) %>% 
  summarize(count = n()) %>%
  mutate(percentage = count/sum(count))

takeout_percentage
```
```{r}
# Check proportion of RestaurantsTableService
tableserv <- yelp_data %>% 
  select(RestaurantsTableService)
summary(tableserv)
```
```{r}
tableserv_percentage <- tableserv %>%
  group_by(RestaurantsTableService) %>% 
  summarize(count = n()) %>%
  mutate(percentage = count/sum(count))

tableserv_percentage
```

```{r}
# Calculate invalid responses (neither dine-in nor takeout)
invalid <- yelp_data %>% 
  filter(RestaurantsTableService == FALSE & RestaurantsTakeOut == FALSE) %>% 
  count()

valid_restaurants <- total_restaurants-invalid

# Calculate service type percentages
takeout_only <- yelp_data %>% 
  filter(RestaurantsTableService == FALSE & RestaurantsTakeOut == TRUE) %>% 
  count()/valid_restaurants

dinein_only <- yelp_data %>% 
  filter(RestaurantsTableService == TRUE & RestaurantsTakeOut == FALSE) %>% 
  count()/valid_restaurants

both <- yelp_data %>% 
  filter(RestaurantsTableService == TRUE & RestaurantsTakeOut == TRUE) %>% 
  count()/valid_restaurants

service_percentage<- data.frame(
  service = c("takeout", "dinein", "both"),
  percentage = c(takeout_only$n, dinein_only$n, both$n), options(digits = 2)
)

 service_percentage
```
According to Ontario restaurant data from Yelp (cite, KSondjaja source), approximately 6% of restaurants
offer dine in service, 32.5% offer takeout, and 61.5% offer both.

## Survey 1
```{r}
set.seed(19)
survey_1 <- survey_1 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))
```

## Survey 2
```{r}
set.seed(19)
survey_2 <- survey_2 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))
```

# Demographic traits of owners

@@

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(revenue = 41975 * rf(num_total,10,5)) %>%
  mutate(factor = abs(rnorm(num_total, 1, .05))) %>%
  mutate(revenue = factor * revenue) %>%
  select(-factor)

@@

survey_2 <-
  bind_rows(
    survey_2 %>%
      filter(service_type == "dinein" & group == "treatment") %>%
      mutate(revenue = 0.55 * revenue)
    ,
    survey_2 %>%
      filter(service_type == "both" & group == "treatment") %>%
      mutate(revenue = 0.83 * revenue)
    ,
    survey_2 %>%
      filter(service_type == "takeout" & group == "treatment") %>%
      mutate(revenue = revenue)
    ,
    survey_2 %>%
      filter(group == "control")
  ) %>%
  arrange(ID)

### 2021-02-17 outputs/paper/paper.Rmd
stitching together simulation work and tidying file names

# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame, 
# and markdown file data_simulation must have been run already

@@

```{r}
treatment_control_groups
```

```{r}
all_units_data
```

```{r}
table_for_surveys
```

>>>>

# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame, 
# and markdown file data_simulation must have been run already

@@

```{r}
treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
treatment_control_groups
```

```{r}
all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
all_units_data
```

```{r}
table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
table_for_surveys
```
